### 2025-04-16 multiple-regression.qmd
20250416 - fix

linearRegressionModel_beta0 <- coef(quadraticTermsRegressionModel)[["(Intercept)"]]
linearRegressionModel_beta1 <- coef(quadraticTermsRegressionModel)[["age"]]
linearRegressionModel_beta2 <- coef(quadraticTermsRegressionModel)[["height"]]
linearRegressionModel_beta3 <- coef(quadraticTermsRegressionModel)[["weight"]]
linearRegressionModel_beta4 <- coef(quadraticTermsRegressionModel)[["target_share"]]
```

>>>>

linearRegressionModel_beta0 <- coef(linearRegressionModel)[["(Intercept)"]]
linearRegressionModel_beta1 <- coef(linearRegressionModel)[["age"]]
linearRegressionModel_beta2 <- coef(linearRegressionModel)[["height"]]
linearRegressionModel_beta3 <- coef(linearRegressionModel)[["weight"]]
linearRegressionModel_beta4 <- coef(linearRegressionModel)[["target_share"]]
```
